Manuscript

### 2017-06-30 manuscript.Rmd
Fixed NYC formatting.
Fixed errors that prevented R Markdown from knitting.

Transform the attribute table into a tibble and select the relevant variables:
```{r show_denverdata}
denver_tracts@data <- tbl_df(tracts@data) %>%
  select(GEOID_TRAC, OBESITY, Park_Percent, PhysAct, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegePercent, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
denver_tracts@data
```

@@

denver_parks_formula <- update(base_formula, . ~ . + park_ls)
```

Locate the centroid of all parks and all census tracts and create a distance matrix:
```{r denver_distancematrix}
denver_tract_centroids <- gCentroid(denver_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
denver_park_centroids <- gCentroid(denver_parks, byid = TRUE)
distance_matrix <- gDistance(denver_tract_centroids, denver_park_centroids, byid = TRUE)
dim(denver_distance_matrix)
```

@@

Transform the attribute table into a tibble and select the relevant variables:
```{r show_bostondata}
tracts@data <- tbl_df(tracts@data) %>%
  select(GEOID10, OBESITY, Phys_Act, MENTAL, Park_Percent, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic)
boston_tracts@data
```

@@

boston_parks_formula <- update(base_formula, . ~ . + park_ls)
```

@@

##New York City

@@

Transform the attribute table into a tibble and select the relevant variables: 
```{r show_nycdata}
nyc_tracts@data <- tbl_df(tracts@data) %>%
  select(GEOID, OBESITY, Park_Percent, Phys_Act, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, Single_Percent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
nyc_tracts@data
```

@@

Create regression equations for use in spatial econometric models:
```{r nyc_equations}
base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegeDeg + Single_Percent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)

parks_formula <- update(base_formula, . ~ . + park_ls)
```

>>>>

Transform the attribute table into a tibble and select the relevant variables:
```{r show_denverdata}
denver_tracts@data <- tbl_df(denver_tracts@data) %>%
  select(GEOID_TRAC, OBESITY, Park_Percent, PhysAct, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegePercent, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
denver_tracts@data
```

@@

denver_parks_formula <- update(denver_base_formula, . ~ . + park_ls)
```

Locate the centroid of all parks and all census tracts and create a distance matrix:
```{r denver_distancematrix}
denver_tract_centroids <- gCentroid(denver_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
denver_park_centroids <- gCentroid(denver_parks, byid = TRUE)
denver_distance_matrix <- gDistance(denver_tract_centroids, denver_park_centroids, byid = TRUE)
dim(denver_distance_matrix)
```

@@

Transform the attribute table into a tibble and select the relevant variables:
```{r show_bostondata}
boston_tracts@data <- tbl_df(boston_tracts@data) %>%
  select(GEOID10, OBESITY, Phys_Act, MENTAL, Park_Percent, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic)
boston_tracts@data
```

@@

boston_parks_formula <- update(boston_base_formula, . ~ . + park_ls)
```

@@

## New York City

@@

Transform the attribute table into a tibble and select the relevant variables: 
```{r show_nycdata}
nyc_tracts@data <- tbl_df(nyc_tracts@data) %>%
  select(GEOID, OBESITY, Park_Percent, Phys_Act, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, Single_Percent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
nyc_tracts@data
```

@@

Create regression equations for use in spatial econometric models:
```{r nyc_equations}
nyc_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegeDeg + Single_Percent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)

nyc_parks_formula <- update(nyc_base_formula, . ~ . + park_ls)
```
